
## Data Processing
### Read Data

The data comes from */BASIL/POSTED/DATA/DERIVED/clean/current/*.  On 9-17-2017, the data was copied to the folder  */BASIL/Projects/DeliriumHarmonization/POSTED/DATA/DERIVED/clean/current/* to make the results reproducible.


```{r}
# dataprocessing <- "R:/POSTED/DATA/DERIVED/clean/processing/"
# dataprocessing <- "/Users/douglastommet/Documents/dwork/BASIL/POSTED/DATA/DERIVED/clean/processing/"

### the analyses/reports up to 20180209 used data from this folder
# dataprocessing <- "/Users/douglastommet/Documents/dwork/BASIL/Projects/DeliriumHarmonization/POSTED/DATA/DERIVED/clean/current/"
dwork.dataprocessing <- path_home("Documents", "dwork", "BASIL", "Projects", "DeliriumHarmonization", "POSTED", "DATA", "DERIVED", "clean", "current")
# filedate <- "-20170917"
filedate <- "-20180117"

inhosp.stata <- "BASIL-Hospital-Patient-Data-Analysis-File"
inhosp.filename <- str_c(inhosp.stata, filedate, ".dta")
patientinterview.stata <- "BASIL-Patient-Interview-Data-Analysis-File"
patientinterview.filename <- str_c(patientinterview.stata, filedate, ".dta")
medical.stata <- "BASIL-Medical-Record-Data-Analysis-File"
medical.filename <- str_c(medical.stata, filedate, ".dta")


# ### 20180220 - Some high severity responses have been reviewed and modified.  The changes havent made their way to the clean data folder yet.  So going to read in the data from the processing folder and update the clean data.
# dataprocessing2 <- "/Users/douglastommet/Documents/dwork/BASIL/POSTED/DATA/DERIVED/clean/processing/"
# filedate2 <- NULL
# inhosp2.stata <- "BASIL-Hospital-Patient-Data-Analysis-File"
# inhosp2.filename <- str_c(inhosp2.stata, filedate2, ".dta")
# inhosp2 <- read_dta(str_c(dataprocessing2, inhosp2.filename))
# inhosp2 <- inhosp2 %>%
#   arrange(studyid, cvpg3a) %>%
#   select(studyid, cvpg3a, starts_with("mdas"), starts_with("drs"), starts_with("camlf"))
  

# This data file contains the delirium severity assessments
inhosp <- read_dta(path(dwork.dataprocessing, inhosp.filename))
inhosp <- inhosp %>%
  arrange(studyid, cvpg3a)

### Only a few cases are changed in the updated data, and it doesn't effect results
# inhosp <- inhosp %>%
#   select(-starts_with("mdas"), -starts_with("drs"), -starts_with("camlf")) %>%
#   bind_cols(inhosp2) 

# This data file contains the vds variables for table 1
patientinterview <- read_dta(path(dwork.dataprocessing, patientinterview.filename)) %>%
  filter(timefr==0) %>%
  select(studyid, timefr, starts_with("vd")) %>%
  select(-vdcamseveritylf, -vdcamseveritysf, -vdmdas, -vddrs)

# This data file contains additional variables for table 1
# Need version 1.1.0 of haven
medical <- read_dta(path(dwork.dataprocessing, medical.filename)) %>%
  mutate(vdsurgical = (basilsc4==2 | hrsurgyn==1)) %>%
  select(studyid, vddementia, vdsurgical, vdcci)

basil <- inhosp %>%
  full_join(patientinterview, by = "studyid") %>%
  full_join(medical, by = "studyid")

foo <- basil %>% select(studyid) %>% dim()
ninterviews <- foo[1]
foo <- basil %>% select(studyid) %>% distinct() %>% dim()
nsubjects <- foo[1]
```

The file has `r nsubjects` subjects and `r ninterviews` interviews.

```{r}

# select baseline hospital visits (cvpg4==1) and daily hospital visits (cvpg4==2)
basil <- basil %>%
  filter(cvpg4==1 | cvpg4==2)

# select complete interviews
basil <- basil %>%
  filter(b_end_of_interview_complete==2)

# select records that are not missing on vds for CAM, MDAS, and DRS
basil <- basil %>%
  filter(!is.na(vdcamseveritylf) & !is.na(vdmdas) & !is.na(vddrs))

# # 11-9-2017 decision: Don't exclude these three subjects.
# # These participants de-enrolled from the study: BD001401, BD000919, BD001102
# basil <- basil %>%
#   filter(!(studyid %in% c("BD001401", "BD000919", "BD001102")))

foo <- basil %>% select(studyid) %>% dim()
ninterviews <- foo[1]
foo <- basil %>% select(studyid) %>% distinct() %>% dim()
nsubjects <- foo[1]
```

This analysis will only use baseline hospital visits and daily hospital visits.  Interviews that are not complete are dropped.  Interviews that are missing the CAM-S vds, the DRS vds, or the MDAS vds are dropped.  ~~There are three subjects that de-enrolled from the study and are dropped from the analysis.~~ [11-9-2017 decision: Do not exclude these three subjecs.]  After applying these filters there are `r nsubjects` subjects and `r ninterviews` interviews remaining in the datafile.



