

## Descriptive statistics

### Summary tables/statistics for DRS (N=`r  dim(basil)[1]`)

#### Original item category frequencies (%)
```{r }
my_sum_function <- function(df) {
  df %>%
    filter(!is.na(y)) %>%
    filter(!is.na(n)) %>%
    summarize(total = sum(n)) %>%
    pull(total)
  
}

basil %>%
  select(starts_with("rdrs")) %>%
  gather(item, y)   %>%
  arrange(item) %>%
  group_by(item, y) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  group_by(item) %>%
  nest() %>%
  mutate(total = map_dbl(data, my_sum_function)) %>%
  unnest(data) %>%
  mutate(per = round(100*n/total, 1)) %>%
  gather(key = stat, value = foo, 4:5) %>%
  mutate(header = ifelse(!is.na(y), str_c(stat, "_", y), str_c(stat, "_NA"))) %>%
  select(-y, -stat) %>%  
  spread(key = header, value = foo) %>%
  replace_na(list(n_0 = 0, n_1 = 0, n_2 = 0, n_3 = 0, n_NA = 0, 
                  per_0 = 0, per_1 = 0, per_2 = 0, per_3 = 0, per_NA = 0)) %>%
  left_join(drs.labels, by = "item") %>%
  select(item, content, total, starts_with("n_"), starts_with("per_")) %>%
  kable(digits = c(0, 0, 0, rep(0, 5), rep(1, 5)), 
        col.names = c("Item", "Content", "Total", 
                      "0", "1", "2", "3", "Missing", 
                      "0", "1", "2", "3", "Missing")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = "left") %>%
  add_header_above(c(" " = 2, "N" = 6, "Percent" = 5))



```

#### Dichotomized item category frequencies (%)

```{r}

basil2 %>%
  select(starts_with("rdrs")) %>%
  gather(item, y)   %>%
  arrange(item) %>%
  group_by(item, y) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  group_by(item) %>%
  nest() %>%
  mutate(total = map_dbl(data, my_sum_function)) %>%
  unnest(data) %>%
  mutate(per = round(100*n/total, 1)) %>%
  gather(key = stat, value = foo, 4:5) %>%
  mutate(header = ifelse(!is.na(y), str_c(stat, "_", y), str_c(stat, "_NA"))) %>%
  select(-y, -stat) %>%  
  spread(key = header, value = foo) %>%
  replace_na(list(n_0 = 0, n_1 = 0, n_NA = 0, 
                  per_0 = 0, per_1 = 0, per_NA = 0)) %>%
  left_join(drs.labels, by = "item") %>%
  select(item, content, total, starts_with("n_"), starts_with("per_")) %>%
  kable(digits = c(0, 0, 0, rep(0, 3), rep(1, 3)), 
        col.names = c("Item", "Content", "Total", 
                      "0", "1", "Missing", 
                      "0", "1", "Missing")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = "left") %>%
  add_header_above(c(" " = 2, "N" = 4, "Percent" = 3))


```

#### Item correlations

```{r}

basil2 %>%
  select(starts_with("rdrs")) %>%
  corrr::correlate() %>%
  kable(digits = 2,
        col.names = c("", "rdrs01", "rdrs02", "rdrs03", "rdrs04", "rdrs05", "rdrs06", "rdrs07", 
                       "rdrs08", "rdrs09", "rdrs10", "rdrs11", "rdrs12", "rdrs13")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = "left")
```

#### Item - total score correlation

Correlation between the item and the sum of the dichotomous items.

```{r}
basil2 %>%
  select(starts_with("rdrs")) %>%
  rowwise() %>%
  mutate(score = sum(c(rdrs01, rdrs02, rdrs03, rdrs04, rdrs05, rdrs06, rdrs07, 
                       rdrs08, rdrs09, rdrs10, rdrs11, rdrs12, rdrs13), na.rm = TRUE)) %>%
  corrr::correlate() %>%
  corrr::focus(score) %>%
  kable(digits = 2,
        col.names = c("", "total score")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = "left")
```

#### Cronbach's alpha

```{r}
basil2 %>%
  select(starts_with("rdrs")) %>%
  psych::alpha(.)

```



### Summary tables/statistics for MDAS (N=`r dim(basil)[1]`)

#### Original item category frequencies (%)

```{r}
basil %>%
  select(starts_with("rmdas")) %>%
  gather(item, y)   %>%
  arrange(item) %>%
  group_by(item, y) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  group_by(item) %>%
  nest() %>%
  mutate(total = map_dbl(data, my_sum_function)) %>%
  unnest(data) %>%
  mutate(per = round(100*n/total, 1)) %>%
  gather(key = stat, value = foo, 4:5) %>%
  mutate(header = ifelse(!is.na(y), str_c(stat, "_", y), str_c(stat, "_NA"))) %>%
  select(-y, -stat) %>%  
  spread(key = header, value = foo) %>%
  replace_na(list(n_0 = 0, n_1 = 0, n_2 = 0, n_3 = 0, n_NA = 0, 
                  per_0 = 0, per_1 = 0, per_2 = 0, per_3 = 0, per_NA = 0)) %>%
  left_join(mdas.labels, by = "item") %>%
  select(item, content, total, starts_with("n_"), starts_with("per_")) %>%
  kable(digits = c(0, 0, 0, rep(0, 5), rep(1, 5)), 
        col.names = c("Item", "Content", "Total", 
                      "0", "1", "2", "3", "Missing", 
                      "0", "1", "2", "3", "Missing")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = "left") %>%
  add_header_above(c(" " = 2, "N" = 6, "Percent" = 5))


```

#### Dichotomized item category frequencies (%)

```{r}

basil2 %>%
  select(starts_with("rmdas")) %>%
  gather(item, y)   %>%
  arrange(item) %>%
  group_by(item, y) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  group_by(item) %>%
  nest() %>%
  mutate(total = map_dbl(data, my_sum_function)) %>%
  unnest(data) %>%
  mutate(per = round(100*n/total, 1)) %>%
  gather(key = stat, value = foo, 4:5) %>%
  mutate(header = ifelse(!is.na(y), str_c(stat, "_", y), str_c(stat, "_NA"))) %>%
  select(-y, -stat) %>%  
  spread(key = header, value = foo) %>%
  replace_na(list(n_0 = 0, n_1 = 0, n_NA = 0, 
                  per_0 = 0, per_1 = 0, per_NA = 0)) %>%
  left_join(mdas.labels, by = "item") %>%
  select(item, content, total, starts_with("n_"), starts_with("per_")) %>%
  kable(digits = c(0, 0, 0, rep(0, 3), rep(1, 3)), 
        col.names = c("Item", "Content", "Total", 
                      "0", "1", "Missing", 
                      "0", "1", "Missing")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = "left") %>%
  add_header_above(c(" " = 2, "N" = 4, "Percent" = 3))


```

#### Item correlations

```{r}

basil2 %>%
  select(starts_with("rmdas")) %>%
  corrr::correlate() %>%
  kable(digits = 2,
        col.names = c("", "rmdas01", "rmdas02", "rmdas03", "rmdas04", "rmdas05", 
                      "rmdas06", "rmdas07", "rmdas08", "rmdas09", "rmdas10")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = "left")
```

#### Item - total score correlation

Correlation between the item and the sum of the dichotomous items.

```{r}
basil2 %>%
  select(starts_with("rmdas")) %>%
  rowwise() %>%
  mutate(score = sum(c(rmdas01, rmdas02, rmdas03, rmdas04, rmdas05, 
                       rmdas06, rmdas07, rmdas08, rmdas09, rmdas10), na.rm = TRUE)) %>%
  corrr::correlate() %>%
  corrr::focus(score) %>%
  kable(digits = 2,
        col.names = c("", "total score")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = "left")
```

#### Cronbach's alpha

```{r}
basil2 %>%
  select(starts_with("rmdas")) %>%
  psych::alpha(.)

```

### Summary tables/statistics for CAM-S (N=`r dim(basil)[1]`)

#### Original item category frequencies (%)

```{r}

basil %>%
  select(starts_with("rcam")) %>%
  select(-rcamlf4a) %>%
  gather(item, y)   %>%
  arrange(item) %>%
  group_by(item, y) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  group_by(item) %>%
  nest() %>%
  mutate(total = map_dbl(data, my_sum_function)) %>%
  unnest(data) %>%
  mutate(per = round(100*n/total, 1)) %>%
  gather(key = stat, value = foo, 4:5) %>%
  mutate(header = ifelse(!is.na(y), str_c(stat, "_", y), str_c(stat, "_NA"))) %>%
  select(-y, -stat) %>%  
  spread(key = header, value = foo) %>%
  replace_na(list(n_0 = 0, n_1 = 0, n_2 = 0, n_NA = 0, 
                  per_0 = 0, per_1 = 0, per_2 = 0, per_NA = 0)) %>%
  left_join(cam.labels, by = "item") %>%
  select(item, content, total, starts_with("n_"), starts_with("per_")) %>%
  kable(digits = c(0, 0, 0, rep(0, 4), rep(1, 4)), 
        col.names = c("Item", "Content", "Total", 
                      "0", "1", "2", "Missing", 
                      "0", "1", "2", "Missing")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = "left") %>%
  add_header_above(c(" " = 2, "N" = 5, "Percent" = 4))


```

#### Dichotomized item category frequency (%)

```{r}
basil2 %>%
  select(starts_with("rcam")) %>%
  select(-rcamlf4a) %>%
  gather(item, y)   %>%
  arrange(item) %>%
  group_by(item, y) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  group_by(item) %>%
  nest() %>%
  mutate(total = map_dbl(data, my_sum_function)) %>%
  unnest(data) %>%
  mutate(per = round(100*n/total, 1)) %>%
  gather(key = stat, value = foo, 4:5) %>%
  mutate(header = ifelse(!is.na(y), str_c(stat, "_", y), str_c(stat, "_NA"))) %>%
  select(-y, -stat) %>%  
  spread(key = header, value = foo) %>%
  replace_na(list(n_0 = 0, n_1 = 0, n_NA = 0, 
                  per_0 = 0, per_1 = 0, per_NA = 0)) %>%
  left_join(cam.labels, by = "item") %>%
  select(item, content, total, starts_with("n_"), starts_with("per_")) %>%
  kable(digits = c(0, 0, 0, rep(0, 3), rep(1, 3)), 
        col.names = c("Item", "Content", "Total", 
                      "0", "1", "Missing", 
                      "0", "1", "Missing")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = "left") %>%
  add_header_above(c(" " = 2, "N" = 4, "Percent" = 3))


```

#### Item correlations

```{r}

basil2 %>%
  select(starts_with("rcam")) %>%
  select(-rcamlf4a) %>%
  corrr::correlate() %>%
  kable(digits = 2,
        col.names = c("", "rcamlf1a", "rcamlf2a", "rcamlf3a", "rcamlf4l", "rcamlf4v", "rcamlf5a", 
                      "rcamlf6a", "rcamlf7a", "rcamlf8a", "rcamlf8d", "rcamlf9a")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = "left")
```

#### Item - total score correlation

Correlation between the item and the sum of the dichotomous items.

```{r}
basil2 %>%
  select(starts_with("rcam")) %>%
  select(-rcamlf4a) %>%
  rowwise() %>%
  mutate(score = sum(c(rcamlf1a, rcamlf2a, rcamlf3a, rcamlf4l, rcamlf4v, rcamlf5a, 
                       rcamlf6a, rcamlf7a, rcamlf8a, rcamlf8d, rcamlf9a), na.rm = TRUE)) %>%
  corrr::correlate() %>%
  corrr::focus(score) %>%
  kable(digits = 2,
        col.names = c("", "total score")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = "left")
```

#### Cronbach's alpha

```{r}
basil2 %>%
  select(starts_with("rcam")) %>%
  select(-rcamlf4a) %>%
  psych::alpha(.)

```


