
## Data Processing
### Read Data

The data comes from */BASIL/POSTED/DATA/DERIVED/clean/current/*.  On 9-17-2017, the data was copied to the folder  */BASIL/Projects/DeliriumHarmonization/POSTED/DATA/DERIVED/clean/current/* to make the results reproducible.


```{r}
# dataprocessing <- "R:/POSTED/DATA/DERIVED/clean/processing/"
# dataprocessing <- "/Users/douglastommet/Documents/dwork/BASIL/POSTED/DATA/DERIVED/clean/processing/"
dataprocessing <- "/Users/douglastommet/Documents/dwork/BASIL/Projects/DeliriumHarmonization/POSTED/DATA/DERIVED/clean/current/"

# This data file contains the delirium severity assessments
inhosp <- read_dta(paste0(dataprocessing, "BASIL-Hospital-Patient-Data-Analysis-File-20170917.dta"))

# This data file contains the vds variables for table 1
patientinterview <- read_dta(paste0(dataprocessing, "BASIL-Patient-Interview-Data-Analysis-File-20170917.dta")) %>%
  filter(timefr==0) %>%
  select(studyid, timefr, starts_with("vd")) %>%
  select(-vdcamseveritylf, -vdcamseveritysf, -vdmdas, -vddrs)

# This data file contains additional variables for table 1
medical <- read_dta(paste0(dataprocessing, "BASIL-Medical-Record-Data-Analysis-File-20170917.dta")) %>%
  select(studyid, vddementia, vdsurgical)

basil <- inhosp %>%
  full_join(patientinterview, by = "studyid") %>%
  full_join(medical, by = "studyid")

foo <- basil %>% select(studyid) %>% dim()
ninterviews <- foo[1]
foo <- basil %>% select(studyid) %>% distinct() %>% dim()
nsubjects <- foo[1]
```

The file has `r nsubjects` subjects and `r ninterviews` interviews.

```{r}

# select baseline hospital visits (cvpg4==1) and daily hospital visits (cvpg4==2)
basil <- basil %>%
  filter(cvpg4==1 | cvpg4==2)

# select complete interviews
basil <- basil %>%
  filter(b_end_of_interview_complete==2)

# select records that are not missing on vds for CAM, MDAS, and DRS
basil <- basil %>%
  filter(!is.na(vdcamseveritylf) & !is.na(vdmdas) & !is.na(vddrs))

# # 11-9-2017 decision: Don't exclude these three subjects.
# # These participants de-enrolled from the study: BD001401, BD000919, BD001102
# basil <- basil %>%
#   filter(!(studyid %in% c("BD001401", "BD000919", "BD001102")))

foo <- basil %>% select(studyid) %>% dim()
ninterviews <- foo[1]
foo <- basil %>% select(studyid) %>% distinct() %>% dim()
nsubjects <- foo[1]
```

This analysis will only use baseline hospital visits and daily hospital visits.  Interviews that are not complete are dropped.  Interviews that are missing the CAM-S vds, the DRS vds, or the MDAS vds are dropped.  ~~There are three subjects that de-enrolled from the study and are dropped from the analysis.~~ [11-9-2017 decision: Do not exclude these three subjecs.]  After applying these filters there are `r nsubjects` subjects and `r ninterviews` interviews remaining in the datafile.



