
### Data recode

The items that were coded as Don't Know, Refused, Uncertain were set to missing, and the response options were reordered such that no symptoms were 0 and any symptoms were positive values.

```{r}

basil <- basil %>%
  mutate(recordid = row_number(),
         rdsi1 = recode(dsi1, "2=1; 1=2; 7=NA; 8=NA; 9=NA;"),
         rdsi1a = recode(dsi1a, "2=1; 1=2; 7=NA; 8=NA; 9=NA;"),
         rdsi2 = recode(dsi2, "2=1; 1=2; 7=NA; 8=NA; 9=NA;"),
         rdsi3 = recode(dsi3, "2=1; 1=2; 7=NA; 8=NA; 9=NA;"),
         rdsi4 = recode(dsi4, "2=1; 1=2; 7=NA; 8=NA; 9=NA;"),
         rdsi5 = recode(dsi5, "2=1; 1=2; 7=NA; 8=NA; 9=NA;"),
         rdsi6 = recode(dsi6, "2=1; 1=2; 7=NA; 8=NA; 9=NA;"),
         rdsi7 = recode(dsi7, "2=1; 1=2; 7=NA; 8=NA; 9=NA;"),
         rdsi8 = recode(dsi8, "2=1; 1=2; 7=NA; 8=NA; 9=NA;"),
         rdsi7a = recode(dsi7a, "9=NA;"),
         rdsi8a = recode(dsi8a, "9=NA;"),
         rcfnq1 = recode(cfnq1, "2=1; 1=2; 7=NA; 8=NA; 11=NA;"),
         rcfnq2 = recode(cfnq2, "2=1; 1=2; 7=NA; 8=NA; 11=NA;"),
         rcfnq3 = recode(cfnq3, "2=1; 1=2; 7=NA; 8=NA; 11=NA;"),
         rcfnq4 = recode(cfnq4, "2=1; 1=2; 7=NA; 8=NA; 11=NA;"),
         rdenq1 = recode(denq1, "2=1; 1=2; 3=NA; 7=NA; 8=NA; 11=NA;"),
         rdenq2 = recode(denq2, "2=1; 1=2; 3=NA; 7=NA; 8=NA; 11=NA;"),
         rdenq3 = recode(denq3, "2=1; 1=2; 3=NA; 7=NA; 8=NA; 11=NA;"),
         rdenq4 = recode(denq4, "2=1; 1=2; 3=NA; 7=NA; 8=NA; 11=NA;"),
         rdenq5 = recode(denq5, "2=1; 1=2; 3=NA; 7=NA; 8=NA; 11=NA;"),
         rdenq6 = recode(denq6, "2=1; 1=2; 3=NA; 7=NA; 8=NA; 11=NA;"),
         rdenq7 = recode(denq7, "2=1; 1=2; 3=NA; 7=NA; 8=NA; 11=NA;"),
         rebnq1 = recode(ebnq1, "2=1; 1=2; 7=NA; 8=NA; 11=NA;"),
         rebnq2 = recode(ebnq2, "2=1; 1=2; 7=NA; 8=NA; 11=NA;"),
         rebnq3 = recode(ebnq3, "2=1; 1=2; 7=NA; 8=NA; 11=NA;"),
         rebnq4 = recode(ebnq4, "2=1; 1=2; 7=NA; 8=NA; 11=NA;"),
         rebnq5 = recode(ebnq5, "2=1; 1=2; 7=NA; 8=NA; 11=NA;"),
         rebnq6 = recode(ebnq6, "2=1; 1=2; 7=NA; 8=NA; 11=NA;"),
         rebnq7 = recode(ebnq7, "2=1; 1=2; 7=NA; 8=NA; 11=NA;"),
         rebnq8 = recode(ebnq8, "2=1; 1=2; 7=NA; 8=NA; 11=NA;"),
         rseva2 = recode(seva2, "2=1; 1=2; 3=NA; "),
         rseva3 = recode(seva3, "2=1; 1=2; 3=NA; "),
         rseva4 = recode(seva4, "2=1; 1=2; 3=NA; "),
         rsevb3 = recode(sevb3, "2=1; 1=2; 3=NA; "),
         rsevb4 = recode(sevb4, "2=1; 1=2; 3=NA; "),
         rsevb5 = recode(sevb5, "13=1; 12=2; 14=3; 11=4; 15=5; "),
         rsevc3 = recode(sevc3, "2=1; 1=2; 3=NA; "),
         rsevd1 = recode(sevd1, "1=1; 2=2; 3=3;  4=NA;"),
         rsevd2 = recode(sevd2, "1=1; 2=2; 3=3;  4=NA;"),
         rsevf2 = recode(sevf2, "1=1; 2=2; 3=3;  4=NA; "),
         rsevg2 = recode(sevg2, "2=1; 1=2; 3=NA; "),
         rsevj1 = recode(sevj1, "6=1; 5=2; 7=NA; "),
         rangir1 = recode(angir1, "2=1; 1=2; 8=NA; "),
         rangir2 = recode(angir2, "2=1; 1=2; 8=NA; "),
         rangir3 = recode(angir3, "2=1; 1=2; 8=NA; "),
         ranxty1 = recode(anxty1, "2=1; 1=2; 8=NA; "),
         ranxty2 = recode(anxty2, "2=1; 1=2; 8=NA; "),
         ranxty3 = recode(anxty3, "2=1; 1=2; 8=NA; "),
         ranxty4 = recode(anxty4, "2=1; 1=2; 8=NA; "),
         ranxty5 = recode(anxty5, "2=1; 1=2; 8=NA; "),
         rdepre1 = recode(depre1, "1=1; 2=2; 8=NA; "),
         rdepre2 = recode(depre2, "1=1; 2=2; 8=NA; "),
         rdepre3 = recode(depre3, "1=1; 2=2; 8=NA; "),
         remotn1 = recode(emotn1, "2=1; 1=2; 8=NA; "),
         remotn2 = recode(emotn2, "2=1; 1=2; 8=NA; "),
         remotn3 = recode(emotn3, "2=1; 1=2; 8=NA; "),
         rcamlf1a = recode(camlf1a, "2=0; 1=1; 3=NA;"),
         rcamlf2a = recode(camlf2a, "1=0; 2=1; 3=2; 4=NA;"),
         rcamlf3a = recode(camlf3a, "1=0; 2=1; 3=2; 4=NA;"),
         rcamlf4a = recode(camlf4a, "1=0; 2=1; 3=2; 4=2;"),
         rcamlf5a = recode(camlf5a, "1=0; 2=1; 3=2; 4=NA;"),
         rcamlf6a = recode(camlf6a, "1=0; 2=1; 3=2; 4=NA;"),
         rcamlf7a = recode(camlf7a, "1=0; 2=1; 3=2; 4=NA;"),
         rcamlf8a = recode(camlf8a, "1=0; 2=1; 3=2; 4=NA;"),
         rcamlf8d = recode(camlf8d, "1=0; 2=1; 3=2; 4=NA;"),
         rcamlf9a = recode(camlf9a, "2=0; 0=1; 1=2; 3=NA;"),
         rmdas01 = recode(mdas01, "3=NA;"),
         rmdas02 = recode(mdas02, "8=NA;"),
         rmdas03 = recode(mdas03, "8=NA;"),
         rmdas04 = recode(mdas04, "8=NA;"),
         rmdas05 = recode(mdas05, "8=NA;"),
         rmdas06 = recode(mdas06, "8=NA;"),
         rmdas07 = recode(mdas07, "8=NA;"),
         rmdas08 = recode(mdas08, "8=NA;"),
         rmdas09 = recode(mdas09, "8=NA;"),
         rmdas10 = recode(mdas10, "8=NA;"),
         rdrs01 = recode(drs01, "8=NA;"),
         rdrs02 = recode(drs02, "8=NA;"),
         rdrs03 = recode(drs03, "8=NA;"),
         rdrs04 = recode(drs04, "8=NA;"),
         rdrs05 = recode(drs05, "8=NA;"),
         rdrs06 = recode(drs06, "8=NA;"),
         rdrs07 = recode(drs07, "8=NA;"),
         rdrs08 = recode(drs08, "8=NA;"),
         rdrs09 = recode(drs09, "8=NA;"),
         rdrs10 = recode(drs10, "8=NA;"),
         rdrs11 = recode(drs11, "8=NA;"),
         rdrs12 = recode(drs12, "8=NA;"),
         rdrs13 = recode(drs13, "8=NA;"),
         rconf =  recode(conf, "10=9;"))

```
  
The DRS, MDAS, CAM-S items are dichotomized to None vs Any symptom.

It is always possible once the item parameters are calibrated in the dichotomous setting to go back to the polytomous response setting.  However, there should be at least 5% in the response categories and that is not always the case.  So, we may end up in a situation where some items are dichotomous and others are polytomous.  This makes the interpretation more difficult.
  
```{r}
basil2 <- basil %>%
  mutate(rdrs01 = recode(rdrs01, "1=0; 2=1; 3=1; "),
         rdrs02 = recode(rdrs02, "1=1; 2=1; 3=1; "),
         rdrs03 = recode(rdrs03, "1=1; 2=1; 3=1; "),
         rdrs04 = recode(rdrs04, "1=1; 2=1; 3=1; "),
         rdrs05 = recode(rdrs05, "1=1; 2=1; 3=1; "),
         rdrs06 = recode(rdrs06, "1=1; 2=1; 3=1; "),
         rdrs07 = recode(rdrs07, "1=1; 2=1; 3=1; "),
         rdrs08 = recode(rdrs08, "1=1; 2=1; 3=1; "),
         rdrs09 = recode(rdrs09, "1=1; 2=1; 3=1; "),
         rdrs10 = recode(rdrs10, "1=1; 2=1; 3=1; "),
         rdrs11 = recode(rdrs11, "1=1; 2=1; 3=1; "),
         rdrs12 = recode(rdrs12, "1=1; 2=1; 3=1; "),
         rdrs13 = recode(rdrs13, "1=1; 2=1; 3=1; "),
         rmdas01 = recode(rmdas01, "1=1; 2=1; 3=1; "),
         rmdas02 = recode(rmdas02, "1=1; 2=1; 3=1; "),
         rmdas03 = recode(rmdas03, "1=1; 2=1; 3=1; "),
         rmdas04 = recode(rmdas04, "1=1; 2=1; 3=1; "),
         rmdas05 = recode(rmdas05, "1=1; 2=1; 3=1; "),
         rmdas06 = recode(rmdas06, "1=1; 2=1; 3=1; "),
         rmdas07 = recode(rmdas07, "1=1; 2=1; 3=1; "),
         rmdas08 = recode(rmdas08, "1=1; 2=1; 3=1; "),
         rmdas09 = recode(rmdas09, "1=1; 2=1; 3=1; "),
         rmdas10 = recode(rmdas10, "1=0; 2=1; 3=1; "),
         rcamlf1a = recode(rcamlf1a, "1=1; 2=1; "),
         rcamlf2a = recode(rcamlf2a, "1=1; 2=1; "),
         rcamlf3a = recode(rcamlf3a, "1=1; 2=1; "),
         rcamlf4a = recode(rcamlf4a, "1=1; 2=1; "),
         rcamlf5a = recode(rcamlf5a, "1=1; 2=1; "),
         rcamlf6a = recode(rcamlf6a, "1=1; 2=1; "),
         rcamlf7a = recode(rcamlf7a, "1=1; 2=1; "),
         rcamlf8a = recode(rcamlf8a, "1=1; 2=1; "),
         rcamlf8d = recode(rcamlf8d, "1=1; 2=1; "),
         rcamlf9a = recode(rcamlf9a, "1=0; 2=1; "))

```

### Item reference table

This table is a reference for the following tables to link item numbers to item content

### DRS

| Item   | Content                                       |
|--------|-----------------------------------------------|
| rdrs01 | Sleep-wake cycle disturbance                  | 
| rdrs02 | Perceptual disturbances and hallucinations    | 
| rdrs03 | Delusions                                     | 
| rdrs04 | Lability of affect                            | 
| rdrs05 | Language                                      | 
| rdrs06 | Thought process abnormalities                 | 
| rdrs07 | Motor agitation                               | 
| rdrs08 | Motor retardation                             | 
| rdrs09 | Orientation                                   | 
| rdrs10 | Attention                                     |  
| rdrs11 | Short-term memory                             | 
| rdrs12 | Long-term memory                              | 
| rdrs13 | Visuospatial ability                          | 

### MDAS

| Item    | Content                                          |
|---------|--------------------------------------------------|
| rmdas01 | Reduced level of consciousness (Awareness)       | 
| rmdas02 | Disorientation                                   | 
| rmdas03 | Short-term memory impairment                     | 
| rmdas04 | Impaired digit span                              | 
| rmdas05 | Reduced ability to maintain and shift attention  | 
| rmdas06 | Disorganized thinking                            | 
| rmdas07 | Perceptual disturbance                           | 
| rmdas08 | Delusions                                        | 
| rmdas09 | Decreased or increased psychomotor activity      | 
| rmdas10 | Sleep-wake cycle disturbance                     |  

### CAM-S

| Item     | Content                        |
|----------|--------------------------------|
| rcamlf1a | Acute change                   | 
| rcamlf2a | Inattention                    | 
| rcamlf3a | Disorganized thinking          | 
| rcamlf4a | Altered level of consciousness | 
| rcamlf5a | Disorientation                 | 
| rcamlf6a | Memory impairment              | 
| rcamlf7a | Perceptual disturbances        | 
| rcamlf8a | Psychomotor agitation          | 
| rcamlf8d | Psychomotor retardation        | 
| rcamlf9a | Sleep-wake cycle disturbance   | 

