
```{r}
loopReplace <- function(text, replacements) {
  for (v in names(replacements)) {
    text <- gsub(sprintf("\\[\\[%s\\]\\]", v), replacements[[v]], text)
  }
  return(text)
}

```

```{r}

  
fit.2pl <- function(x, y, instrument, modeltype, use.variables1, use.variables2, st.analysis, st.variable, savefscores){
  
  instrument.variables1 <- use.variables1[! use.variables1 %in% c("recordid", "studyid", "studyidnum")]
  instrument.variables1.free <- instrument.variables1
  instrument.variables1.free[1] <- paste0(instrument.variables1.free[1], "*")
  nitems.model1 <- length(instrument.variables1)

  model1 <- paste0("f by ", instrument.variables1.free, ";")
  model1.collapsed<- paste0(model1, collapse = " \n ")
  model1 <- paste(model1.collapsed, "\n", "f @1;")
  
  cfa.1.body <- mplusObject(
    ANALYSIS = st.analysis,
    VARIABLE = st.variable,
    MODEL = model1,
    OUTPUT = "standardized;",
    SAVEDATA = "",
    usevariables = use.variables1,
    rdata = x
  )
  cfa.1.fit <- mplusModeler(cfa.1.body, 
                                modelout = paste0("cfa-", instrument, "-1-", y, "-", modeltype, ".inp"), 
                            run = TRUE,
                            hashfilename = FALSE)
  
  param <- readModels(paste0("cfa-", instrument, "-1-", y, "-", modeltype, ".out"))$parameters$unstandardized
  mc.param <- param %>%
    filter(paramHeader=="F.BY" | 
           paramHeader=="Thresholds" |
           (paramHeader=="Variances" & param=="F")) %>%
    mutate(est = as.numeric(est)) %>%
    mutate_all(funs(tolower))

  mc.param <- mc.param[1:(2*nitems.model1+1), 1:3]
  
  myParam <- data.frame(f1s = 0)
  for (i in 1:dim(mc.param)[1]) {
    if (mc.param$paramHeader[i]=="f.by") {
      myParam[[paste0("f",i, "s")]] = paste0(gsub("\\.", " ", 
                                                  mc.param$paramHeader[i]), " ",
                                            mc.param$param[i], 
                                            "@", mc.param$est[i])
    }
    if (mc.param$paramHeader[i]=="thresholds") {
      myParam[[paste0("f",i, "s")]] = paste0("[", mc.param$param[i], 
                                             "@", mc.param$est[i],"]")
    }
    if (mc.param$paramHeader[i]=="variances") {
      myParam[[paste0("f",i, "s")]] = paste0(mc.param$param[i], 
                                             "*")
    }
  }

  goo <- paste(paste0("[[f", 1:dim(mc.param)[1], "s]];"), collapse = " \n ")
  model2 <- loopReplace(goo, myParam)
  
  varlist2 <- paste0("f by ", use.variables2, ";")
  varlist2.collapsed<- paste0(varlist2, collapse = " \n ")
  model2 <- paste(model2, "\n", varlist2.collapsed)
  
  fscores.filename <- paste0("fscores-", instrument, "-2-", y, ".dat")
  if (savefscores==TRUE) {
    savedata2 <- paste("save = fscores; file =", fscores.filename, ";")
  } else {
    savedata2 <- c("")
  }
  

  cfa.2.body <- mplusObject(
    ANALYSIS = st.analysis,
    VARIABLE = st.variable,
    MODEL = model2,
    OUTPUT = "standardized;",
    SAVEDATA = savedata2,
    usevariables = c(use.variables1, use.variables2),
    rdata = x)
  cfa.2.fit <- mplusModeler(cfa.2.body, 
                                 modelout = paste0("cfa-", instrument, "-2-", y, "-", modeltype,".inp"), 
                            run = TRUE,
                            hashfilename = FALSE)
  
}

fit.3pl <- function(x, y, instrument, use.variables1, use.variables2, st.analysis, st.variable){
  
  instrument.variables1 <- use.variables1[! use.variables1 %in% c("recordid", "studyid", "studyidnum")]
  instrument.variables1.free <- instrument.variables1
  instrument.variables1.free[1] <- paste0(instrument.variables1.free[1], "*")
  nitems.model1 <- length(instrument.variables1)

  instrument.variables2 <- use.variables2[! use.variables1 %in% c("recordid", "studyidnum")]
  nitems.model2 <- length(instrument.variables2)

  model1 <- paste0("f by ", instrument.variables1.free, ";")
  model1.collapsed<- paste0(model1, collapse = " \n ")
  model1 <- paste(model1.collapsed, "\n", "f @1;")
  
  model1.thresh <- paste0("[", instrument.variables1[1], "$2-", instrument.variables1[nitems.model1], 
                          "$2] (a1-a", nitems.model1, ");")
  model1.priors <- paste0("a1-a", nitems.model1, "~N(1.386, 1);")
  model1 <- paste(model1, "\n", model1.thresh, "\n", "MODEL PRIORS:", "\n", model1.priors)
  

  cfa.1.body <- mplusObject(
    ANALYSIS = st.analysis,
    VARIABLE = st.variable,
    MODEL = model1,
    OUTPUT = "",
    SAVEDATA = "",
    usevariables = use.variables1,
    rdata = x
  )
  cfa.1.fit <- mplusModeler(cfa.1.body, 
                              modelout = paste0("cfa-", instrument, "-1-", y,"-3pl.inp"), run = TRUE)

  param <- extractModelParameters(paste0("cfa-", instrument, "-1-", y,"-3pl.out"))$unstandardized
  mc.param <- param %>%
    filter(paramHeader=="F.BY" |
           paramHeader=="Thresholds" |
           (paramHeader=="Variances" & param=="F")) %>%
    mutate(est = as.numeric(est)) %>%
    mutate_all(funs(tolower))

  mc.param <- unique(mc.param[,1:3])

  myParam <- data.frame(f1s = 0)
  for (i in 1:dim(mc.param)[1]) {
    if (mc.param$paramHeader[i]=="f.by") {
      myParam[[paste0("f",i, "s")]] = paste0(gsub("\\.", " ",
                                                  mc.param$paramHeader[i]), " ",
                                            mc.param$param[i],
                                            "@", mc.param$est[i])
    }
    if (mc.param$paramHeader[i]=="thresholds") {
      myParam[[paste0("f",i, "s")]] = paste0("[", mc.param$param[i],
                                             "@", mc.param$est[i],"]")
    }
    if (mc.param$paramHeader[i]=="variances") {
      myParam[[paste0("f",i, "s")]] = paste0(mc.param$param[i],
                                             "*")
    }
  }

  goo <- paste(paste0("[[f", 1:dim(mc.param)[1], "s]];"), collapse = " \n ")
  model.2 <- loopReplace(goo, myParam)

  
  varlist2 <- paste0("f by ", use.variables2, ";")
  
  
  model2.thresh <- paste0("[", instrument.variables2[1], "$2-", instrument.variables2[nitems.model2], 
                          "$2] (a1-a", nitems.model2, ");")
  model2.priors <- paste0("a1-a", nitems.model2, "~N(1.386, 1);")
  varlist2 <- paste(varlist2, model2.thresh, "MODEL PRIORS:", model2.priors)
  varlist2.collapsed<- paste0(varlist2, collapse = " \n ")
  model2 <- paste(model2, "\n", varlist2.collapsed)

  fscores.filename <- paste0("fscores-", instrument, "-2-", y, "-3pl.dat")
  savedata2 <- paste("save = fscores; file =", fscores.filename, ";")

  cfa.2.body <- mplusObject(
    ANALYSIS = st.analysis,
    VARIABLE = st.variable,
    MODEL = model2,
    OUTPUT = "",
    SAVEDATA = savedata2,
    usevariables = c(use.variables1, use.variables2),
    rdata = x)
  cfa.2.fit <- mplusModeler(cfa.2.body,
                               modelout = paste0("cfa-", instrument, "-2-", y,"-3pl.inp"), run = TRUE)
  
  
  
}

```


```{r}


df1 <- basil2
sim_list <- list(df1)
index_list <- 1


# Mplus commands in common across the three instruments
mplus.variable <- "idvariable = recordid; cluster = studyidnum; CATEGORICAL ARE all;"
mplus.analysis.2pl <- "estimator = mlr; link=logit; type=complex;"
mplus.analysis.wlsmv <- "estimator = wlsmv; type=complex;"

## DRS
use.variables1.drs <- c("recordid", "studyidnum", "rdrs01", "rdrs02", "rdrs06", "rdrs07", "rdrs08", 
                     "rdrs09", "rdrs10", "rdrs11")
use.variables2.drs <- c("rdrs03", "rdrs04", "rdrs05", "rdrs12", "rdrs13")

### Fit a 2PL model
foo<- map2(sim_list, index_list, fit.2pl, 
           instrument = "drs", 
           modeltype = "2pl",
           use.variables1 = use.variables1.drs,
           use.variables2 = use.variables2.drs,
           st.analysis = mplus.analysis.2pl,
           st.variable = mplus.variable,
           savefscores = TRUE)

### Fit a 2PL model with WLSMV to get fit statistics
foo<- map2(sim_list, index_list, fit.2pl, 
           instrument = "drs", 
           modeltype = "wlsmv",
           use.variables1 = use.variables1.drs,
           use.variables2 = use.variables2.drs,
           st.analysis = mplus.analysis.wlsmv,
           st.variable = mplus.variable,
           savefscores = FALSE)

# ### Fit a 3PL model
# mplus.analysis.3pl <- "estimator = mlr; link=logit; type=complex;"
# mplus.variable.3pl <- "idvariable = recordid; cluster = studyidnum; CATEGORICAL ARE all (3pl);"
# 
# foo<- map2(sim_list, index_list, fit.3pl, 
#            instrument = "drs", 
#            use.variables1 = use.variables1.drs,
#            use.variables2 = use.variables2.drs,
#            st.analysis = mplus.analysis.3pl,
#            st.variable = mplus.variable.3pl)

## MDAS
use.variables1.mdas <- c("recordid", "studyidnum", "rmdas02", "rmdas03", "rmdas04", "rmdas05", 
                        "rmdas06", "rmdas07", "rmdas09", "rmdas10")
use.variables2.mdas <- c("rmdas01", "rmdas08")

### Fit a 2PL model
foo<- map2(sim_list, index_list, fit.2pl, 
           instrument = "mdas", 
           modeltype = "2pl",
           use.variables1 = use.variables1.mdas,
           use.variables2 = use.variables2.mdas,
           st.analysis = mplus.analysis.2pl,
           st.variable = mplus.variable,
           savefscores = TRUE)

### Fit a 2PL model with WLSMV to get fit statistics
foo<- map2(sim_list, index_list, fit.2pl, 
           instrument = "mdas", 
           modeltype = "wlsmv",
           use.variables1 = use.variables1.mdas,
           use.variables2 = use.variables2.mdas,
           st.analysis = mplus.analysis.wlsmv,
           st.variable = mplus.variable,
           savefscores = FALSE)

# ### Fit a 3PL model
# mplus.analysis.3pl <- "estimator = mlr; link=logit; type=complex;"
# mplus.variable.3pl <- "idvariable = recordid; cluster = studyidnum; CATEGORICAL ARE all (3pl);"
# 
# foo<- map2(sim_list, index_list, fit.3pl, 
#            instrument = "mdas", 
#            use.variables1 = use.variables1.mdas,
#            use.variables2 = use.variables2.mdas,
#            st.analysis = mplus.analysis.3pl,
#            st.variable = mplus.variable.3pl)

## CAM
use.variables1.cam <- c("recordid", "studyidnum", "rcamlf2a", "rcamlf3a", "rcamlf5a", "rcamlf6a", 
                        "rcamlf7a", "rcamlf8a", "rcamlf8d", "rcamlf9a")
use.variables2.cam <- c("rcamlf1a", "rcamlf4a")

### Fit a 2PL model
foo<- map2(sim_list, index_list, fit.2pl, 
           instrument = "cam", 
           modeltype = "2pl",
           use.variables1 = use.variables1.cam,
           use.variables2 = use.variables2.cam,
           st.analysis = mplus.analysis.2pl,
           st.variable = mplus.variable,
           savefscores = TRUE)

### Fit a 2PL model with WLSMV to get fit statistics
foo<- map2(sim_list, index_list, fit.2pl, 
           instrument = "cam", 
           modeltype = "wlsmv",
           use.variables1 = use.variables1.cam,
           use.variables2 = use.variables2.cam,
           st.analysis = mplus.analysis.wlsmv,
           st.variable = mplus.variable,
           savefscores = FALSE)

# ### Fit a 3PL model
# mplus.analysis.3pl <- "estimator = mlr; link=logit; type=complex;"
# mplus.variable.3pl <- "idvariable = recordid; cluster = studyidnum; CATEGORICAL ARE all (3pl);"
# 
# foo<- map2(sim_list, index_list, fit.3pl, 
#            instrument = "cam", 
#            use.variables1 = use.variables1.cam,
#            use.variables2 = use.variables2.cam,
#            st.analysis = mplus.analysis.3pl,
#            st.variable = mplus.variable.3pl)

```

## Model Fitting (Dichotomous model)

### Fit CFA models
We will fit a CFA in the MDAS, DRS, and CAM-S individually then equate them.  To ensure that the CFA covers the same dimension for each test, we are fitting the CFA to a core set of items in common across test and then add in the remaining items keeping the core item parameters fixed.

The core set of items are: 

| Feature                           | DRS          | MDAS           |  CAM-S  |
|-----------------------------------|--------------|----------------|-------|
| Sleep disturbance                 | drs01        | mdas10         | camlf9a |
| Perceptual disturbance            | drs02        | mdas07         | camlf7a |
| Psychomotor agitation/retardation | drs07, drs08 | mdas09         | camlf8a, camlf8d |
| Orientation                       | drs09        | mdas02         | camlf5a |
| Attention                         | drs10        | mdas04, mdas05 | camlf2a |
| Memory impairment                 | drs11, drs12 | mdas03         | camlf6a |
| Disorganized thinking/thought process abnormalities | drs06 | mdas06 | camlf3a |

**NOTE:**  In the original 2PL models, the sleep item did not fit well.  To try to improve the fit, we tried changing to a 3PL model.  This did not improve the fit.  So, next we changed the way we dichotomized sleep.  Instead of grouping the categories 0 vs 1, 2, 3, we used 0, 1 vs 2, 3.  This helped improve the fit in the DRS and MDAS a lot and in the CAM-S a little.

### DRS Confirmatory Factor Analysis
#### Fit statistics
Model 1
```{r}
readModels("cfa-drs-1-1-wlsmv.out")$summaries %>%
  select(Observations, CFI, RMSEA_Estimate) %>%
  kable(digits=2, col.names = c("N", "CFI", "RMSEA")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = "center")
```

Model 2
```{r}
readModels("cfa-drs-2-1-wlsmv.out")$summaries %>%
  select(Observations, CFI, RMSEA_Estimate) %>%
  kable(digits=2, col.names = c("N", "CFI", "RMSEA")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = "center")
  

```


#### Item Parameters
Model 1
```{r}
item.parameter.table("cfa-drs-1-1-2pl.out", 8)
```

Model 2
```{r}
item.parameter.table("cfa-drs-2-1-2pl.out", 13)
```



```{r}
omega.drs <- myomega("cfa-drs-2-1-2pl.out") %>% round(2)

```
The McDonald's omega statistic for the DRS is `r  omega.drs`.

### MDAS Confirmatory Factor Analysis
#### Fit statistics
Model 1
```{r}
readModels("cfa-mdas-1-1-wlsmv.out")$summaries %>%
  select(Observations, CFI, RMSEA_Estimate) %>%
  kable(digits=2, col.names = c("N", "CFI", "RMSEA")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = "center")
  

```

Model 2
```{r}
readModels("cfa-mdas-2-1-wlsmv.out")$summaries %>%
  select(Observations, CFI, RMSEA_Estimate) %>%
  kable(digits=2, col.names = c("N", "CFI", "RMSEA")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = "center")
  

```

#### Item Parameters
Model 1
```{r}
item.parameter.table("cfa-mdas-1-1-2pl.out", 8)
```

Model 2
```{r}
item.parameter.table("cfa-mdas-2-1-2pl.out", 10)
```

```{r}
omega.mdas <- myomega("cfa-mdas-2-1-2pl.out") %>% round(2)

```
The McDonald's omega statistic for the MDAS is `r  omega.mdas`.

### CAM-S Confirmatory Factor Analysis
#### Fit statistics
Model 1
```{r}
readModels("cfa-cam-1-1-wlsmv.out")$summaries %>%
  select(Observations, CFI, RMSEA_Estimate) %>%
  kable(digits=2, col.names = c("N", "CFI", "RMSEA")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = "center")
  

```

Model 2
```{r}
readModels("cfa-cam-2-1-wlsmv.out")$summaries %>%
  select(Observations, CFI, RMSEA_Estimate) %>%
  kable(digits=2, col.names = c("N", "CFI", "RMSEA")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F, position = "center")
  

```

#### Item Parameters
Model 1
```{r}
item.parameter.table("cfa-cam-1-1-2pl.out", 8)

```

Model 2
```{r}
item.parameter.table("cfa-cam-2-1-2pl.out", 10)
```

```{r}
omega.cam <- myomega("cfa-cam-2-1-2pl.out") %>% round(2)

```
The McDonald's omega statistic for the CAM-S is `r  omega.cam`.


