## Item equating
Using the SNSequate package to equate item parameters.


```{r}
# drs.par.dich <- readModels("cfa-drs-2-1-2pl.out", quiet = TRUE)$parameters$unstandardized
# 
# drs.par.dich <- drs.par.dich %>%
#       filter(paramHeader=="F.BY" | 
#            paramHeader=="Thresholds") %>%
#     mutate(est = as.numeric(est),
#            item = ifelse(paramHeader=="Thresholds", 
#                         str_split_fixed(param, "\\$1", 2), param),
#            parameter = ifelse(paramHeader=="Thresholds", "T", "FL")) %>%
#     select(parameter, item, est) %>%
#     mutate_all(funs(tolower))
#   drs.par.dich <- drs.par.dich[1:26,1:3]
#   drs.par.dich$est <- as.numeric(drs.par.dich$est)
#   
# drs.par.dich <- drs.par.dich %>% 
#   spread(parameter, est) %>%
#   mutate(B.drs = t/fl,
#          A.drs = fl,
#          C.drs = 0,
#          itemnum = row_number()) %>%
#   select(item, itemnum, A.drs, B.drs, C.drs)
#       
# 
# mdas.par.dich <- readModels("cfa-mdas-2-1-2pl.out", quiet = TRUE)$parameters$unstandardized
# 
# mdas.par.dich <- mdas.par.dich %>%
#       filter(paramHeader=="F.BY" | 
#            paramHeader=="Thresholds") %>%
#     mutate(est = as.numeric(est),
#            item = ifelse(paramHeader=="Thresholds", 
#                         str_split_fixed(param, "\\$1", 2), param),
#            parameter = ifelse(paramHeader=="Thresholds", "T", "FL")) %>%
#     select(parameter, item, est) %>%
#     mutate_all(funs(tolower))
#   mdas.par.dich <- mdas.par.dich[1:20,1:3]
#   mdas.par.dich$est <- as.numeric(mdas.par.dich$est)
#   
# mdas.par.dich <- mdas.par.dich %>% 
#   spread(parameter, est) %>%
#   mutate(B.mdas = t/fl,
#          A.mdas = fl,
#          C.mdas = 0) %>%
#   select(item, A.mdas, B.mdas, C.mdas)
# mdas.par.dich$itemnum <- c(14, 9, 11, 16, 17, 18, 2, 3, 21, 1)
# 
# 
# cam.par.dich <- readModels("cfa-cam-2-1-2pl.out", quiet = TRUE)$parameters$unstandardized
# 
# cam.par.dich <- cam.par.dich %>%
#       filter(paramHeader=="F.BY" | 
#            paramHeader=="Thresholds") %>%
#     mutate(est = as.numeric(est),
#            item = ifelse(paramHeader=="Thresholds", 
#                         str_split_fixed(param, "\\$1", 2), param),
#            parameter = ifelse(paramHeader=="Thresholds", "T", "FL")) %>%
#     select(parameter, item, est) %>%
#     mutate_all(funs(tolower))
#   cam.par.dich <- cam.par.dich[1:20,1:3]
#   cam.par.dich$est <- as.numeric(cam.par.dich$est)
#   
# cam.par.dich <- cam.par.dich %>% 
#   spread(parameter, est) %>%
#   mutate(B.cam = t/fl,
#          A.cam = fl,
#          C.cam = 0,
#          itemnum = row_number()) %>%
#   select(item, itemnum, A.cam, B.cam, C.cam)
# cam.par.dich$itemnum <- c(22, 10, 24, 25, 9, 26, 2, 7, 8, 1)
                     

getIRTparam <- function(filename, instrument, itemnum) {
  par.dich <- readModels(filename, quiet = TRUE)$parameters$unstandardized

  par.dich <- par.dich %>%
    filter(paramHeader=="F.BY" | 
           paramHeader=="Thresholds") %>%
    mutate(est = as.numeric(est),
           item = ifelse(paramHeader=="Thresholds", 
                        str_split_fixed(param, "\\$1", 2), param),
           parameter = ifelse(paramHeader=="Thresholds", "T", "FL")) %>%
    select(parameter, item, est) %>%
    mutate_all(funs(tolower))

  par.dich$est <- as.numeric(par.dich$est)
  
  
  par.dich <- par.dich %>% 
    spread(parameter, est) %>%
    mutate(B = t/fl,
           A = fl,
           C = 0) %>%
    select(item, A, B, C)
  par.dich$itemnum <- itemnum
  
  par.names <- c("item", paste0("A.", instrument), paste0("B.", instrument), paste0("C.", instrument), "itemnum")
  names(par.dich) <- par.names
  
  return(par.dich)
}

# drs.par.dich <- getIRTparam("cfa-drs-2-1-2pl.out", "drs", 1:13)
# mdas.par.dich <- getIRTparam("cfa-mdas-2-1-2pl.out", "mdas", c(14, 9, 11, 16, 17, 18, 2, 3, 21, 1))
# cam.par.dich <- getIRTparam("cfa-cam-2-1-2pl.out", "cam", c(22, 10, 24, 25, 9, 26, 2, 7, 8, 1))

# Including "thought process abnormalities" in the linking
# drs.par.dich <- getIRTparam("cfa-drs-2-1-2pl.out", "drs", 1:13)
# mdas.par.dich <- getIRTparam("cfa-mdas-2-1-2pl.out", "mdas", c(14, 9, 11, 16, 17, 6, 2, 3, 21, 1))
# cam.par.dich <- getIRTparam("cfa-cam-2-1-2pl.out", "cam", c(22, 10, 6, 25, 9, 11, 2, 7, 8, 1))

# split cam4a - level of consciousness into 2 items
drs.par.dich <- getIRTparam("cfa-drs-2-1-2pl.out", "drs", 1:13)
mdas.par.dich <- getIRTparam("cfa-mdas-2-1-2pl.out", "mdas", c(14, 9, 11, 16, 17, 6, 2, 3, 21, 1))
cam.par.dich <- getIRTparam("cfa-cam-2-1-2pl.out", "cam", c(22, 10, 6, 25, 26,  9, 11, 2, 7, 8, 1))



```


### DRS item parameters
```{r}
drs.par.foo <- item.parameter.df.poly("cfa-drs-2-1-2pl.out", 1, "drs")
item.parameter.table.poly(drs.par.foo, 1, "DRS")

```

### MDAS item parameters
```{r}
mdas.par.foo <- item.parameter.df.poly("cfa-mdas-2-1-2pl.out", 1, "mdas")
item.parameter.table.poly(mdas.par.foo, 1, "MDAS")

```

### CAM-S item parameters
```{r}
cam.par.foo <- item.parameter.df.poly("cfa-cam-2-1-2pl.out", 1, "cam")
item.parameter.table.poly(cam.par.foo, 1, "CAM")

```


The items used to link the MDAS to the DRS are: Disorientation, Perceptual disturbance, Sleep/wake cycle disturbance, Short term memory impairment, Delusions, and Thought process abnormality/Disorganized thinking.

The items used to link the CAM-S to the DRS are: Disorientation, Perceptual disturbance, Sleep/wake cycle disturbance, Psychomotor agitation, Psychomotor retardation, Attention, and Thought process abnormality/Disorganized thinking.

```{r}
# Function equating instrument 2 to instrument 1
# df1 & df2 are data frames from the the getIRTparam function
# comitems are a vector of the common items between instruments
# instrument.name1, instrument.name2 are character strings that match the instrument names in df1, df2. eg. "drs", "mdas", "cam"
linkingFunction <- function(df1, df2, comitems, instrument.name1, instrument.name2) {
  names <- colnames(df2)
  par.df1.df2 <- full_join(df1, df2, by = "itemnum") 
  
  par.df1.df2 <- par.df1.df2[, c(paste0("A.", instrument.name1),
                                 paste0("B.", instrument.name1),
                                 paste0("C.", instrument.name1),
                                 paste0("A.", instrument.name2),
                                 paste0("B.", instrument.name2),
                                 paste0("C.", instrument.name2))]

  link.df1.df2 <- irt.link(par.df1.df2, comitems, model = "3PL", icc = "logistic", D = 1.7)

  A.link <- link.df1.df2$Haebara[1]
  B.link <- link.df1.df2$Haebara[2]

  df2$A.l <- df2[,2]*A.link
  df2$B.l <- (df2[,3] - B.link)/A.link
  df2$fl.l <- df2$A.l
  df2$t.l <- df2$B.l*df2$fl.l

  
  names(df2) <- c(names,
                  paste0("A.l.", instrument.name2),
                  paste0("B.l.", instrument.name2),
                  paste0("fl.l.", instrument.name2),
                  paste0("t.l.", instrument.name2) )

  df2
}


```

```{r} 
# df1 - item parameters from linkingFunction
item.parameter.table3 <- function(df, instrument.name){
  
  foo <- df[, c("item", 
                paste0("A.", instrument.name), 
                paste0("B.", instrument.name), 
                paste0("A.l.", instrument.name), 
                paste0("B.l.", instrument.name))]

  foo %>%
    kable(caption = paste("Comparision between original and linked item parameters for", instrument.name),
          digits = 2,
          col.names = c("Item", "A (original)", "B (original)", "A (linked)", "B (linked)")) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F, position = "left")
  
}



```

```{r}
# Fit a 2PL CFA model with item parameters fixed to the parameters in df1
# Mostly useful to get an Mplus output file with the item parameters set to the equated values
# x - the data frame, or a list of data frames
# y - the data frame index number
# df1 - data frame of item parameters from linkingFunction
# use.variables1, use.variables2 - vector of the variables to use
# st.analysis, st.variable - character strings to pass to Mplus analysis and variable commands
# savefscores - should fscores be saved?

fit.2pl.linked <- function(x, y, df1, instrument, use.variables1, use.variables2, st.analysis, st.variable, savefscores){
  
  foo <- df1 %>%
    mutate(fl.param = item,
           t.param = paste0(item, "$1"),
           fl.parH = "f.by",
           t.parH = "thresholds") %>%
    select(fl.parH, fl.param, starts_with("fl.l."), t.parH, t.param, starts_with("t.l."))

  foo.fl <- foo[,1:3]
  foo.t <- foo[,4:6]
  colnames(foo.fl) <- c("paramHeader", "param", "est")
  colnames(foo.t) <- c("paramHeader", "param", "est")

  goo <- rbind(foo.fl, foo.t)

  myParam <- data.frame(f1s = 0)
  for (i in 1:dim(goo)[1]) {
    if (goo$paramHeader[i]=="f.by") {
        myParam[[paste0("f",i, "s")]] = 
          paste0(gsub("\\.", " ", goo$paramHeader[i]), " ", goo$param[i], "@", goo$est[i])
    }
    if (goo$paramHeader[i]=="thresholds") {
      myParam[[paste0("f",i, "s")]] = paste0("[", goo$param[i], "@", goo$est[i],"]")
    }
    if (goo$paramHeader[i]=="variances") {
      myParam[[paste0("f",i, "s")]] = paste0(goo$param[i], "@", goo$est[i])
    }
  }
  hoo <- paste(paste0("[[f", 1:dim(goo)[1], "s]];"), collapse = " \n ")

  model.linked <- loopReplace(hoo, myParam)

  fscores.filename <- paste0("fscores-", instrument, "-linked-", y, ".dat")
  if (savefscores==TRUE) {
    savedata2 <- paste("save = fscores; file =", fscores.filename, ";")
  } else {
    savedata2 <- c("")
  }
    
  cfa.link.body <- mplusObject(
    ANALYSIS = st.analysis,
    VARIABLE = st.variable,
    MODEL = model.linked,
    OUTPUT = "",
    SAVEDATA = savedata2,
    usevariables = c(use.variables1, use.variables2),
    rdata = x)
  cfa.link.fit <- mplusModeler(cfa.link.body, 
                               modelout = paste0("cfa-", instrument, "-link-", y,".inp"),
                               run = TRUE, hashfilename = FALSE, writeData = "always")

  
  
}


```


```{r}
comitems <- c(1, 2, 3, 6, 9, 11)
mdas.par.dich <- linkingFunction(drs.par.dich, mdas.par.dich, comitems, "drs", "mdas")

## These should be carried over from 005a-fit-cfa-models.Rmd
# df1 <- basil2
# sim_list <- list(df1)
# index_list <- 1
# 
# 
# # Mplus commands in common across the three instruments
# mplus.variable <- "idvariable = recordid; cluster = studyidnum; CATEGORICAL ARE all;"
# mplus.analysis.2pl <- "estimator = mlr; link=logit; type=complex;"
# mplus.analysis.wlsmv <- "estimator = wlsmv; type=complex;"
# 
# use.variables1.mdas <- c("recordid", "studyidnum", "rmdas02", "rmdas03", "rmdas04", "rmdas05", 
#                         "rmdas06", "rmdas07", "rmdas09", "rmdas10")
# use.variables2.mdas <- c("rmdas01", "rmdas08")

### Fit a 2PL model with the equated parameters
foo<- map2(sim_list, index_list, fit.2pl.linked,
           df1 = mdas.par.dich,
           instrument = "mdas", 
           use.variables1 = use.variables1.mdas,
           use.variables2 = use.variables2.mdas,
           st.analysis = mplus.analysis.2pl,
           st.variable = mplus.variable,
           savefscores = TRUE)

```

### MDAS item parameters linked

```{r}
item.parameter.table3(mdas.par.dich, "mdas")

```


```{r}
comitems <- c(1, 2, 6, 7, 8, 9, 10, 11)
cam.par.dich <- linkingFunction(drs.par.dich, cam.par.dich, comitems, "drs", "cam")


### Fit a 2PL model with the equated parameters
foo<- map2(sim_list, index_list, fit.2pl.linked,
           df1 = cam.par.dich,
           instrument = "cam", 
           use.variables1 = use.variables1.cam,
           use.variables2 = use.variables2.cam,
           st.analysis = mplus.analysis.2pl,
           st.variable = mplus.variable,
           savefscores = TRUE)

```

### CAM-S item parameters linked

```{r}
item.parameter.table3(cam.par.dich, "cam")

```






