
### Information plots using only first threshold

These analyses explore the contribution the second and third thresholds have on the overall information levels of the instruments.  

#### Figure S1: Test Information Curve using only the first threshold 

```{r}

testinfo <- drs.info.poly %>%
  select(theta, info.sens) %>%
  rename(drsinfo = info.sens) %>%
  left_join(mdas.info.poly %>% 
              select(theta, info.sens) %>%
              rename(mdasinfo = info.sens), by="theta") %>%
  left_join(camlf.info.poly %>%
              select(theta, info.sens) %>%
              rename(camlfinfo = info.sens), by="theta") %>%
  gather(test, info, 2:4)



ggplot(testinfo, aes(theta, info, group=test, color=test)) +
  geom_line() +
  scale_color_brewer(palette = "Dark2", 
                     name = "Delirium Instrument",
                     breaks = c("drsinfo", "mdasinfo", "camlfinfo"),
                     labels = c("DRS", "MDAS", "CAM-S LF")) + 
  scale_y_continuous("Information", breaks=seq(0,12,2)) +
  scale_x_continuous("Delirium Intensity", breaks=seq(-4,8,1)) +
  ggtitle("Test Information Curves (Polytomous CFA, first threshold only)") +
  theme_doug()

```

#### Figure S2: Difference in Information curves between dichotomous and polytomous outcomes
```{r}

testinfo <- drs.info.poly %>%
  select(theta, info.diff) %>%
  rename(drsinfo = info.diff) %>%
  left_join(mdas.info.poly %>% 
              select(theta, info.diff) %>%
              rename(mdasinfo = info.diff), by="theta") %>%
  left_join(camlf.info.poly %>%
              select(theta, info.diff) %>%
              rename(camlfinfo = info.diff), by="theta") %>%
  gather(test, info, 2:4)



ggplot(testinfo, aes(theta, info, group=test, color=test)) +
  geom_line() +
  scale_color_brewer(palette = "Dark2", 
                     name = "Delirium Instrument",
                     breaks = c("drsinfo", "mdasinfo", "camlfinfo"),
                     labels = c("DRS", "MDAS", "CAM-S LF")) + 
  scale_y_continuous("Information", breaks=seq(0,12,2)) +
  scale_x_continuous("Delirium Intensity", breaks=seq(-4,8,1)) +
  ggtitle("Difference in Test Information Curves") +
  theme_doug()  

```

#### Figure S3: Difference in measurement error between dichotomous and polytomous outcomes

```{r}
fscores.dich.drs <- readModels("cfa-drs-2-1-2pl.out", quiet = TRUE)[["savedata"]] %>%
  setNames(tolower(names(.))) %>%
  select(recordid, f, f_se) %>%
  rename(f.dich.drs = f,
         f_se.dich.drs = f_se)

fscores.dich.mdas <- readModels("cfa-mdas-link-1.out", quiet = TRUE)[["savedata"]] %>%
  setNames(tolower(names(.))) %>%
  select(recordid, f, f_se) %>%
  rename(f.dich.mdas = f,
         f_se.dich.mdas = f_se)

fscores.dich.camlf <- readModels("cfa-cam-link-1.out", quiet = TRUE)[["savedata"]] %>%
  setNames(tolower(names(.))) %>%
  select(recordid, f, f_se) %>%
  rename(f.dich.camlf = f,
         f_se.dich.camlf = f_se)

fscores.poly.drs <- readModels("cfa-drs-3-1.out", quiet = TRUE)[["savedata"]] %>%
  setNames(tolower(names(.))) %>%
  select(recordid, f, f_se) %>%
  rename(f.poly.drs = f,
         f_se.poly.drs = f_se)

fscores.poly.mdas <- readModels("cfa-mdas-3-1.out", quiet = TRUE)[["savedata"]] %>%
  setNames(tolower(names(.))) %>%
  select(recordid, f, f_se) %>%
  rename(f.poly.mdas = f,
         f_se.poly.mdas = f_se)

fscores.poly.camlf <- readModels("cfa-cam-3-1.out", quiet = TRUE)[["savedata"]] %>%
  setNames(tolower(names(.))) %>%
  select(recordid, f, f_se) %>%
  rename(f.poly.camlf = f,
         f_se.poly.camlf = f_se)


fscores <- fscores.dich.drs %>%
  left_join(fscores.dich.mdas, by = "recordid") %>%
  left_join(fscores.dich.camlf,  by = "recordid") %>%
  left_join(fscores.poly.drs,  by = "recordid") %>%
  left_join(fscores.poly.mdas, by = "recordid") %>%
  left_join(fscores.poly.camlf,  by = "recordid") %>%
  mutate(se.diff.drs = f_se.dich.drs - f_se.poly.drs, 
         se.diff.mdas = f_se.dich.mdas - f_se.poly.mdas, 
         se.diff.camlf = f_se.dich.camlf - f_se.poly.camlf)

goo1 <- fscores %>%
  select(recordid, f.poly.drs, f.poly.mdas, f.poly.camlf) %>%
  gather(test, f.poly, 2:4) %>%
  separate(test, sep="f.poly.", into = c("foo1", "test")) %>%
  select(-foo1)

goo2 <- fscores %>%
  select(recordid, se.diff.drs, se.diff.mdas, se.diff.camlf) %>%
  gather(test, se.diff, 2:4) %>%
  separate(test, sep="se.diff.", into = c("foo1", "test")) %>%
  select(-foo1) 

goo3 <- fscores %>%
  select(recordid, f_se.dich.drs, f_se.dich.mdas, f_se.dich.camlf) %>%
  gather(test, se.dich, 2:4) %>%
  separate(test, sep="f_se.dich.", into = c("foo1", "test")) %>%
  select(-foo1) 

goo4 <- fscores %>%
  select(recordid, f_se.poly.drs, f_se.poly.mdas, f_se.poly.camlf) %>%
  gather(test, se.poly, 2:4) %>%
  separate(test, sep="f_se.poly.", into = c("foo1", "test")) %>%
  select(-foo1) 

goo5 <- fscores %>%
  select(recordid, f.dich.drs, f.dich.mdas, f.dich.camlf) %>%
  gather(test, f.dich, 2:4) %>%
  separate(test, sep="f.dich.", into = c("foo1", "test")) %>%
  select(-foo1)

goo <- goo1 %>%
  left_join(goo2, by = c("recordid", "test")) %>%
  left_join(goo3, by = c("recordid", "test")) %>%
  left_join(goo4, by = c("recordid", "test")) %>%
  left_join(goo5, by = c("recordid", "test")) %>%
  select(recordid, test, f.dich, f.poly, se.dich, se.poly, se.diff)
  
  
goo %>%  
  ggplot(aes(x = f.poly, y = se.diff, color=test)) +
    geom_point(alpha=.5) +
    scale_color_brewer(palette = "Dark2", 
                      name = "Delirium Scale",
                      breaks = c("drs", "mdas", "camlf"),
                      labels = c("DRS", "MDAS", "CAM-S LF")) + 
  ylab("Difference in SEM (Dich - Poly)") +
  scale_x_continuous("Delirium Intensity", breaks=seq(-4,8,1), limits =c(-4, 8)) +
  ggtitle("Difference in Standard Error of Measurement") +
  theme_doug()  



```


#### Figure S4: Boxplot of standard error of measurement for dichotomous model (from Mplus)
The delirium intensity has been cut into bins of size = 0.2.  Boxplots of the SEM are shown for each bin.  
```{r}
goo %>%
  mutate(f.binned = cut(f.dich, breaks = seq(-2, 3, by = .2))) %>%
  ggplot(aes(x=f.binned, y=se.dich, color = test)) +
    geom_boxplot(outlier.shape = NA,outlier.colour = NA) +
    scale_color_brewer(palette = "Dark2", 
                      name = "Delirium Scale",
                      breaks = c("drs", "mdas", "camlf"),
                      labels = c("DRS", "MDAS", "CAM-S LF")) + 
    scale_x_discrete("Delirium Intensity", labels = seq(-2, 3, by=.2)) +
    scale_y_continuous("SEM (Dich)", limits = c(.25, 1)) +
    ggtitle("Standard Error of Measurement for dichotomous model (from Mplus)") +
    geom_hline(aes(yintercept = .3), linetype="solid") +
    theme_doug()  

```


#### Figure S5: Boxplot of standard error of measurement for polytomous model (from Mplus)
The delirium intensity has been cut into bins of size = 0.2.  Boxplots of the SEM are shown for each bin. 
```{r}
goo %>%
  mutate(f.binned = cut(f.poly, breaks = seq(-2, 3, by = .2))) %>%
  ggplot(aes(x=f.binned, y=se.poly, color = test)) +
    geom_boxplot(outlier.shape = NA,outlier.colour = NA) +
    scale_color_brewer(palette = "Dark2", 
                      name = "Delirium Scale",
                      breaks = c("drs", "mdas", "camlf"),
                      labels = c("DRS", "MDAS", "CAM-S LF")) + 
    scale_x_discrete("Delirium Intensity", labels = seq(-2, 3, by=.2)) +
    scale_y_continuous("SEM (Poly)", limits = c(.25, 1)) +
    ggtitle("Standard Error of Measurement for polytomous model (from Mplus)") +
    geom_hline(aes(yintercept = .3), linetype="solid") +
    theme_doug()  


```


#### Figure S6: Standard error of measurement for dichotomous model (from Information function)
```{r}
testinfo <- drs.info.poly %>%
  select(theta, sem.sens) %>%
  rename(drssem = sem.sens) %>%
  left_join(mdas.info.poly %>% 
              select(theta, sem.sens) %>%
              rename(mdassem = sem.sens), by="theta") %>%
  left_join(camlf.info.poly %>%
              select(theta, sem.sens) %>%
              rename(camlfsem = sem.sens), by="theta") %>%
  gather(test, sem, 2:4)

testinfo %>%
  ggplot(aes(theta, sem, group=test, color=test)) +
    geom_line() +
    scale_color_brewer(palette = "Dark2", 
                     name = "Delirium Instrument",
                     breaks = c("drssem", "mdassem", "camlfsem"),
                     labels = c("DRS", "MDAS", "CAM-S LF")) + 
    scale_y_continuous("SEM", limits = c(0, 2), breaks=seq(0, 1, .2)) +
    scale_x_continuous("Delirium Intensity", limits = c(-2, 3), breaks=seq(-2, 3, 1)) +
    ggtitle("Standard Error of Measurement for dichotomous model (from Information function)")+
    geom_hline(aes(yintercept = .3), linetype="solid") +
    theme_doug()  


```



#### Figure S7: Standard error of measurement for polytomous model (from Information function)
```{r}
testinfo <- drs.info.poly %>%
  select(theta, sem) %>%
  rename(drssem = sem) %>%
  left_join(mdas.info.poly %>% 
              select(theta, sem) %>%
              rename(mdassem = sem), by="theta") %>%
  left_join(camlf.info.poly %>%
              select(theta, sem) %>%
              rename(camlfsem = sem), by="theta") %>%
  gather(test, sem, 2:4)

testinfo %>%
  ggplot(aes(theta, sem, group=test, color=test)) +
    geom_line() +
    scale_color_brewer(palette = "Dark2", 
                     name = "Delirium Instrument",
                     breaks = c("drssem", "mdassem", "camlfsem"),
                     labels = c("DRS", "MDAS", "CAM-S LF")) + 
    scale_y_continuous("SEM", limits = c(0, 2), breaks=seq(0, 1, .2)) +
    scale_x_continuous("Delirium Intensity", limits = c(-2, 3), breaks=seq(-2, 3, 1)) +
    ggtitle("Standard Error of Measurement for polytomous model (from Information function)") +
    geom_hline(aes(yintercept = .3), linetype="solid") +
    theme_doug()


```


