
## Sensitivity analysis for the non-independence of observations
This sensitivity analysis addresses concerns of the non-independence of multiple observations across subjects.  In this analysis we randomly sampled one observation for each subject and then refit the first two CFA models.  This was repeated 500 times.  The parameter estimates from the n=1178 observations are then compared to this bootstrap-like distribution of parameter estimates.

```{r, eval=FALSE}
index_list <- 1:500
sim_list<- list()

nested_basil2 <- basil2 %>%
    group_by(studyidnum) %>%   
    nest() %>%              
    mutate(n = 1)

for (i in index_list) {
  sim_list[[i]] <- nested_basil2 %>%
    mutate(samp = map2(data, n, sample_n)) %>% 
    select(studyidnum, samp) %>%
    unnest()
  
}


# foo <- split(basil2, basil2$studyid)
# df2 <- lapply(split(df, df$color),
#    function(subdf) subdf[sample(1:nrow(subdf), 3),]
# )
# 
# df2 <- map(foo, function(subdf) subdf[sample(1:nrow(subdf), 1),])


# df1 <- basil2 %>% group_by(studyid) %>% sample_n(1) %>% ungroup()
# df2 <- basil2 %>% group_by(studyid) %>% sample_n(1) %>% ungroup()
# df3 <- basil2 %>% group_by(studyid) %>% sample_n(1) %>% ungroup()
# sim_list <- list(df1, df2, df3)



# for (i in index_list) {
#   sim_list[[i]] <- basil2 %>% group_by(studyid) %>% sample_n(1) %>% ungroup()
#   
# }



### Fit a 2PL model
foo<- map2(sim_list, index_list, fit.2pl, 
           instrument = "drs-boot", 
           modeltype = "2pl",
           use.variables1 = use.variables1.drs,
           use.variables2 = use.variables2.drs,
           st.analysis = mplus.analysis.2pl,
           st.variable = mplus.variable,
           savefscores = FALSE)

## MDAS
# use.variables1.mdas <- c("recordid", "studyidnum", "rmdas02", "rmdas03", "rmdas04", "rmdas05", 
#                         "rmdas07", "rmdas09", "rmdas10")
# use.variables2.mdas <- c("rmdas01", "rmdas06", "rmdas08")

### Fit a 2PL model
foo<- map2(sim_list, index_list, fit.2pl, 
           instrument = "mdas-boot", 
           modeltype = "2pl",
           use.variables1 = use.variables1.mdas,
           use.variables2 = use.variables2.mdas,
           st.analysis = mplus.analysis.2pl,
           st.variable = mplus.variable,
           savefscores = FALSE)

## CAM
# use.variables1.cam <- c("recordid", "studyidnum", "rcamlf2a", "rcamlf5a", "rcamlf6a", 
#                         "rcamlf7a", "rcamlf8a", "rcamlf8d", "rcamlf9a")
# use.variables2.cam <- c("rcamlf1a", "rcamlf3a", "rcamlf4a")

### Fit a 2PL model
foo<- map2(sim_list, index_list, fit.2pl, 
           instrument = "cam-boot", 
           modeltype = "2pl",
           use.variables1 = use.variables1.cam,
           use.variables2 = use.variables2.cam,
           st.analysis = mplus.analysis.2pl,
           st.variable = mplus.variable,
           savefscores = FALSE)
```

```{r}

bootSummaryTable <- function(boot.df, param.df, instrument.name, par, par.name){
  
  foo <- boot.df[, c("item", paste(par))]
  colnames(foo) <- c("item", "par")
  summary.table <- foo %>%
    group_by(item) %>%
    summarize(A.mean = mean(par),
              A.sd   = sd(par),
              A.0    = quantile(par, 0),
              A.25   = quantile(par, 0.25),
              A.50   = quantile(par, 0.50),
              A.75   = quantile(par, 0.75),
              A.100  = quantile(par, 1))
  
  param.df[, c("item", paste(par))] %>%
    left_join(summary.table, by = "item") %>%
    kable(caption = paste("Summary of", par.name, "parameters for the", instrument.name),
          col.names= c("Item", "Full sample parameter estimate", "Mean", "SD", "Min", "p25", "Median", "p75", "Max"),
          digits = c(0, 2, rep(2, 7))) %>%
    column_spec(2, width = "10em")
  
}

bootSummaryPlot <- function(boot.df, param.df, instrument.name, par, par.name, ylim){
  ggplot(boot.df, aes_string(x = "item", y = par)) + 
  geom_boxplot() +
  coord_cartesian(ylim = ylim) +
  geom_point(data = param.df, aes_string(x = "item", y = par), color="red", size=2) +
  labs(x = "Item", 
       y = paste(par.name, "parameter"), 
       title = paste("Summary plot of", par.name, "parameters for", instrument.name))

  
}


```

```{r}


files.drs <- list.files(pattern = "drs-boot-2-([0-9]|[0-9][0-9]|[0-9][0-9][0-9])-2pl.out") 
dat2.drs <- map(files.drs, getIRTparam, "drs", 1:13)
dat2DF.drs <- map2_df(dat2.drs, files.drs, ~update_list(.x, file = .y))

### Summary tables for DRS
bootSummaryTable(dat2DF.drs, drs.par.dich, "DRS", "A.drs", "A")
bootSummaryTable(dat2DF.drs, drs.par.dich, "DRS", "B.drs", "B")

### Summary plots for DRS
bootSummaryPlot(dat2DF.drs, drs.par.dich, "DRS", "A.drs", "A", c(0, 7))
bootSummaryPlot(dat2DF.drs, drs.par.dich, "DRS", "B.drs", "B", c(-2, 8))


```

```{r}

files.mdas <- list.files(pattern = "mdas-boot-2-([0-9]|[0-9][0-9]|[0-9][0-9][0-9])-2pl.out") 
dat2.mdas <- map(files.mdas, getIRTparam, "mdas", c(14, 9, 11, 16, 17, 18, 2, 3, 21, 1))
dat2DF.mdas <- map2_df(dat2.mdas, files.mdas, ~update_list(.x, file = .y))

### Summary tables for MDAS
bootSummaryTable(dat2DF.mdas, mdas.par.dich, "MDAS", "A.mdas", "A")
bootSummaryTable(dat2DF.mdas, mdas.par.dich, "MDAS", "B.mdas", "B")
 
### Summary plots for MDAS
bootSummaryPlot(dat2DF.mdas, mdas.par.dich, "MDAS", "A.mdas", "A", c(0, 7))
bootSummaryPlot(dat2DF.mdas, mdas.par.dich, "MDAS", "B.mdas", "B", c(-2, 8))


```

```{r}

files.cam <- list.files(pattern = "cam-boot-2-([0-9]|[0-9][0-9]|[0-9][0-9][0-9])-2pl.out") 
dat2.cam <- map(files.cam, getIRTparam, "cam", c(22, 10, 24, 25, 9, 26, 2, 7, 8, 1))
dat2DF.cam <- map2_df(dat2.cam, files.cam, ~update_list(.x, file = .y))

### Summary tables for CAM
bootSummaryTable(dat2DF.cam, cam.par.dich, "CAM", "A.cam", "A")
bootSummaryTable(dat2DF.cam, cam.par.dich, "CAM", "B.cam", "B")

### Summary plots for CAM
bootSummaryPlot(dat2DF.cam, cam.par.dich, "CAM", "A.cam", "A", c(0, 7))
bootSummaryPlot(dat2DF.cam, cam.par.dich, "CAM", "B.cam", "B", c(-2, 8))


```
